The Splashback Radius of Planck-SZ clusters

### 2018-11-15 Paper_new/RSP_paper_new.tex
minor edits

Given the mass of the halo, the location of the splashback radius
constitutes a direct probe of the halo accretion rate. Motivated by
these studies, \citet{more2016detection} attempted to detect this
feature in observations. Using the optically selected Sloan Digital
Sky Survey RedMaPPer galaxy cluster catalog
\citep{rykoff2014redmapper}, and by cross-correlating it with the
SDSS photometric galaxy sample, \citet{more2016detection} found evidence
for the steepening of the dark matter density profile, and therefore
the splashback radius of this sample of galaxy clusters (further
corroborated by including further models for mis-centering by
\citet{baxter2017halo} and in the Dark Energy Survey data by
\citet{chang2017splashback}). Somewhat surprisingly,
\citet{more2016detection} found that the location of the splashback
radius was inconsistent with that expected from numerical
simulations of dark matter by about $20\pm5$\%. Although they
investigated potential systematic issues, they did not have access
to mock cluster catalogs which could mimic the selection effects of
optically-identified clusters. \citet{busch2017assembly} used a
simplified optical cluster selection algorithm on the Millennium
simulation, and pointed out that optical clusters can be heavily
affected by projection issues, and could potentially introduce
systematics in the inference of the splashback radius, as well as
halo assembly bias. The existence of projection effects in the
optical cluster catalog in the context of halo assembly bias was 
also demonstrated by \citet{zu2016level}.

>>>>

Given the mass of the halo, the location of the splashback radius
constitutes a direct probe of the halo accretion rate. Motivated by
these studies, \citet{more2016detection} attempted to detect this
feature in observations. Using the optically selected Sloan Digital
Sky Survey RedMaPPer galaxy cluster catalog
\citep{rykoff2014redmapper}, and by cross-correlating it with the
SDSS photometric galaxy sample, \citet{more2016detection} found evidence
for the steepening of the dark matter density profile, and therefore
the splashback radius of this sample of galaxy clusters. This was 
corroborated by including further models for mis-centering by
\citet{baxter2017halo} and in the Dark Energy Survey data by
\citet{chang2017splashback} using optically selected clusters. Somewhat surprisingly,
\citet{more2016detection} found that the location of the splashback radius was
inconsistent with that expected from numerical simulations of dark matter by
about $20\pm5$\% (see also \citet{baxter2017halo, chang2017splashback}).
Although they
investigated potential systematic issues, they did not have access
to mock cluster catalogs which could mimic the selection effects of
optically-identified clusters. \citet{busch2017assembly} used a
simplified optical cluster selection algorithm on the Millennium
simulation, and pointed out that optical clusters can be heavily
affected by projection issues, and could potentially introduce
systematics in the inference of the splashback radius, as well as
halo assembly bias. The existence of projection effects in the
optical cluster catalog in the context of halo assembly bias was 
also demonstrated by \citet{zu2016level}.
